Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-30 cbm-rbd-paper.tex
subsections in sec 6, other stuff

As can be seen there and in the numerical examples in Section~\ref{sec:examples} below,
for continuous component lifetime distributions,
$\tausnow$ is a smooth function of $\tnow$ during periods where no component fails,
with discrete jumps at component failure times.
The size of the jump depends on the relevance of the failed component for the current system reliability.
Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model, as we assume component failures to be mutually independent
given the Weibull parameters.
Common cause failures will seriously influence the RLD and thus $\tausnow$,
and we will comment on possible extensions in the Outlook (Section~\ref{sec:outlook}).

@@

\begin{SCfigure}
\centering
\includegraphics[width=0.5\textwidth]{tauhist1fig2T}
\caption[t]{$\tausnow$, $\tstarnow = \tnow + \tausnow$ and $\gstarnow = \gnow(\tausnow)$
%and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
$\tausnow$ (top panel) decrease weakens and attains a near-constant speed from about $\tnow = 2$ during failure-free periods,
with discrete drops at the failures of components $P_2$, $P_3$ and $H$ only.
%With the failure of $H$ at time $\tnow = 8$,
$\tausnow$ falls below $\delta = 0.1$ at time $\tnow = 6$,
triggering preventive maintenance of the system.
$\tausnow = 1.60$ at $\tnow = 0$, this corresponds to the optimal maintenance time
in an age-based policy that takes the system as monolithic. 
Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
the cost-optimal moment of maintenance on the absolute timescale (center panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
showing that as time progresses, accumulated information indicates that maintenance can be postponed.
Consequently, $\gstarnow$ (bottom panel) is steadily decreasing,
with small upward jumps at the failures of $P_2$ and $P_3$.
%so the drops in $\tausnow$ do not entirely outweigh the higher likelihood of system failure
%due to the failure of these components.
%\textbf{***show $\Rsysnow(\tausnow)$???}
At $\tnow = 6$, the expected unit cost rate is $0.033$,
and so considerably lower than the expected cost rate of $0.2 / 1.6 = 0.125$
for an age-based policy not accounting for component information.}
\label{fig:tauhist1fig2T}
\end{SCfigure}

@@

As illustrative example for a system with complex layout,
we use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
see Figure~\ref{fig:brakesys-layout}.
In all subsequent examples of this section,
prior component model parameters are taken as in Table~\ref{tab:priorparams}.

@@

Note that the scale parameter for component type H is $1$,
such that failure times for this component type are assumed to follow an Exponential distribution.
In cases where only $H$ and one or both of $P_3$ and $P_4$ are functioning,
the system reliability function will thus be close to exponential,
making preventive maintenance unattractive.

@@

The cost parameters are chosen as $c_u = 1$, $c_p = 0.2$ in all examples,
i.e., corrective maintenance is five times more costly than preventive maintenance.
This makes it worthwile to aim for a preventive repair of the system,
but corrective maintenance will not be avoided at all cost.
Indeed, $c_u / c_p = 5$ means that risking corrective maintenance is worthwile
if one can expect to utilize the system five times longer
than under a predictive maintenance schedule.

Below, we illustrate our procedure under three different exemplary failure time histories;
a more systematic simulation study is subsequently presented in Section~\ref{sec:sim}.

@@

In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
and follow the system until $\tnow = 2$ only.
Here, components of type $C$ behave more or less as expected,
while type $P$ components fail quite early.
Overall, prior assumptions are reasonably in line with observed failure behaviour.
%with a slight tendency to earlier failures.
Consequently, the difference between the continuous update case and the no update case is small,
as visualized in Figure~\ref{fig:tauhist2fig3T}.
***$\tausnow$ values are slightly lower when component parameters are updated,
reflecting the slightly too early failures of type $P$ components.
Due to recommending maintenance to be carried out a bit earlier,
prospective and total cost rate are slightly higher than in the no update case.
However, these differences are minuscule in comparison to the gains offered by the continuous update
in case of the first failure history
(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3T} and \ref{fig:tauhist2fig3T}).

@@

%The third failure history contains very late failures for all component types
%by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
%and following the system until $\tnow = 14$.
%The late failure times for type $C$ components are especially surprising,
%with the prior predictive reliability being $0.01$ at time $10$
%(see top left panel of Figure~\ref{fig:compprior1fig1}).
%Here, the situation is more extreme than in the first failure history.
%Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
%$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
%For the model without update, $\tausnow$ steadily decreases instead,
%ignoring any information on component behaviour to be gained during the current system run.
%Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
%with only $P_2$ having failed by then, and all other components up and running,
%corresponding to a considerable waste of component lifetime.
%
%\begin{figure}
%\includegraphics[width=\textwidth]{tauhist3fig3}
%\caption{Effect of the continuous parameter update for the third failure history,
%containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
%\label{fig:tauhist3fig3}
%\end{figure}

The third failure history contains very early failures
with $C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$,
and we follow the system until $\tnow = 0.5$.

@@

***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
unlike in other scenarios, overall trend for $\tausnow$ constant because of heavy drops,
costs are underestimated without update***

@@

***$\tthresh$ could vary over time, e.g., longer on weekends or outside office hours

***$\tprep$ instead of $\tthresh$: always too late when scheduling maintenance once $\tausnow < \tprep$.
Problem common to all CBM policies? usually no preparation time assumed?

>>>>

As can be seen there and in the numerical examples in Section~\ref{sec:examples} below,
for continuous component lifetime distributions,
$\tausnow$ is a smooth function of $\tnow$ during periods where no component fails,
with discrete jumps at component failure times.
The size of the jump depends on the relevance of the failed component for the current system reliability.
Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model, as we assume component failures to be mutually independent
given the component model parameters.
Common cause failures will seriously influence the RLD and thus $\tausnow$,
and we will comment on possible extensions in the Outlook (Section~\ref{sec:outlook}).

@@

\begin{figure}
%\centering
\includegraphics[width=\textwidth]{tauhist1fig2T}
\caption[t]{$\tausnow$, $\tstarnow = \tnow + \tausnow$ and $\gstarnow = \gnow(\tausnow)$
%and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
$\tausnow$ (top panel) decrease weakens and attains a near-constant speed from about $\tnow = 2$ during failure-free periods,
with discrete drops at the failures of components $P_2$, $P_3$ and $H$ only.
%With the failure of $H$ at time $\tnow = 8$,
$\tausnow$ falls below $\delta = 0.1$ at time $\tnow = 6$,
triggering preventive maintenance of the system.
$\tausnow = 1.60$ at $\tnow = 0$, this corresponds to the optimal maintenance time
in an age-based policy that takes the system as monolithic. 
Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
the cost-optimal moment of maintenance on the absolute timescale (center panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
showing that as time progresses, accumulated information indicates that maintenance can be postponed.
Consequently, $\gstarnow$ (bottom panel) is steadily decreasing,
with small upward jumps at the failures of $P_2$ and $P_3$.
%so the drops in $\tausnow$ do not entirely outweigh the higher likelihood of system failure
%due to the failure of these components.
%\textbf{***show $\Rsysnow(\tausnow)$???}
At $\tnow = 6$, the expected unit cost rate is $0.033$,
and so considerably lower than the expected cost rate of $0.2 / 1.6 = 0.125$
for an age-based policy not accounting for component information.}
\label{fig:tauhist1fig2T}
\end{figure}

@@

We now elucidate in more detail the case study used for the previous illustrative figures.
We use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
see Figure~\ref{fig:brakesys-layout}.

The cost parameters are chosen as $c_u = 1$, $c_p = 0.2$, % in all examples,
i.e., corrective maintenance is five times more costly than preventive maintenance.
This makes it worthwile to aim for a preventive repair of the system,
but corrective maintenance will not be avoided at all cost.
%Indeed, $c_u / c_p = 5$ means that risking corrective maintenance is worthwile
%if one can expect to run the system five times longer
%than the preventive maintenance interval.

The choice of prior parameters for the four component models are discussed in Section~\ref{sec:ex-prior};
then, our maintenance policy is illustrated under three different exemplary failure time histories,
described in Sections~\ref{sec:ex-1}, \ref{sec:ex-2} and \ref{sec:ex-3}.
A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.

@@

\subsection{Prior component models}
\label{sec:ex-prior}

The prior component model parameters chosen for this case study
are given in Table~\ref{tab:priorparams}.
Note that the scale parameter for component type H is $1$,
such that failure times for this component type are assumed to follow an Exponential distribution.
In cases where only $H$ and one or both of $P_3$ and $P_4$ are functioning,
the system reliability function will thus be close to exponential,
making preventive maintenance unattractive.

@@

\subsection{Failure history 1: failures later than expected}
\label{sec:ex-1}

@@

\subsection{Failure history 2: failure times as expected}
\label{sec:ex-2}

In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
and follow the system until $\tnow = 2.5$ only.
Here, components of type $C$ behave more or less as expected,
while type $P$ components fail slightly earlier than expected.
Overall, prior assumptions are reasonably in line with observed failure behaviour.
%with a slight tendency to earlier failures.
Consequently, the difference between the continuous update case and the no update case is small,
as visualized in Figure~\ref{fig:tauhist2fig3T}.
***$\tausnow$ values for the model with parameter updates vary around those obtained without parameter updates,
same for $\tstarnow$ and $\gstarnow$.
Model with update suggests to mainatin a bit earlier,
since $\tausnow$ drops below $\delta = 0.1$ at $\tnow = ***$,
while this happens for the no update model at $\tnow = ***$.

However, these differences are very small in comparison to the gains offered by the continuous update
in case of the first failure history
(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3T} and \ref{fig:tauhist2fig3T}).

@@

\subsection{Failure history 3: failures earlier than expected}
\label{sec:ex-3}

%The third failure history contains very late failures for all component types
%by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
%and following the system until $\tnow = 14$.
%The late failure times for type $C$ components are especially surprising,
%with the prior predictive reliability being $0.01$ at time $10$
%(see top left panel of Figure~\ref{fig:compprior1fig1}).
%Here, the situation is more extreme than in the first failure history.
%Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
%$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
%For the model without update, $\tausnow$ steadily decreases instead,
%ignoring any information on component behaviour to be gained during the current system run.
%Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
%with only $P_2$ having failed by then, and all other components up and running,
%corresponding to a considerable waste of component lifetime.
%
%\begin{figure}
%\includegraphics[width=\textwidth]{tauhist3fig3}
%\caption{Effect of the continuous parameter update for the third failure history,
%containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
%\label{fig:tauhist3fig3}
%\end{figure}
%
The third failure history contains very early failures
with $C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$,
and we follow the system until $\tnow = 0.5$***0.75?.

@@

***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
unlike in other scenarios, overall trend for $\tstarnow$ constant because of heavy drops,
costs are underestimated without update***

@@
